%-------------------------
% Resume in LateX
% Author : Abhin Mankalale
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Abhin Mankalale} & Email: \href{mailto:catchabhinmr@gmail.com}{catchabhinmr@gmail.com}\\
  \href{}{} & Mobile: \href{tel:+919552608760}{+91-9552608760} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart    
    \resumeSubheading
      {Birla Institute of Technology and Science}{Goa, India}
      {Bachelor of Engineering in Electrical and Electronics; }{Aug 2015 -- July 2019}
  \resumeSubHeadingListEnd
%
%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Java, Python, JavaScript, SQL}
      \hfill
      \textbf{Technologies}{: GCP, AWS, Angular,GITHUB Action, Springboot, TeamCity, Grafana}
    }
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

          
% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 -- Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd

%-------------------------------------------

    \resumeSubheading
      {Deustche Bank}{Bangalore, Karnataka}
      {Associate Software Engineer}{March 2022 - November 2024}
      \resumeItemListStart
        \resumeItem{Monitoring}
          {Implemented an end-to-end monitoring and reporting solution for cloud applications, harnessing the capabilities of Google Cloud Platform APIs & Grafana to gather and visualize crucial performance metrics across the organization.}
        \resumeItem{Toil}
          {Developed the bank's SRE support automation solution using Python Flask, Angular, Shell, TFE & GitHub Actions, eliminating over 300 hours of toil per month}
        \resumeItem{Workflows}
          {Implemented CI/CD pipelines with GitHub Actions, resulting in a 60\% reduction in deployment time, integrated them with the SDLC & Veracode pipelines for quality checks & evidence collection.}
       

    \resumeSubheading
      {Deustche Bank}{Bangalore, Karnataka}
      {Technology Analyst}{July 2019 - March 2022}
      \resumeItemListStart
        \resumeItem{Automation}
          {Designed and upgraded the self-service VM modification tool (eliminating the need for tedious manual vendor process & costs) and reduced the turnaround time for upgrades from 3 weeks to ~5 minutes.} 
        \resumeItem{Automation}
          {Implemented custom VM segregation & placement logic (having dedicated hosts for Linux & Windows) reducing ESXI & Microsoft licensing costs which helped save over €2.2 million yearly.} 
        \resumeItem{Automation}
          {Implemented Automation pipelines with Automic, for resolving priority incidents, which will help resolve issues on server outages.} 
        \resumeItem{CI-CD pipeline}
          {Incorporated Continuous Integration and Delivery through TeamCity to the project pipeline that has automated the application deployment process. It has reduced the time for deployment by 90\%}
        \resumeItem{Security}
          {Updated the old methodology for handling developer credentials in the codebase with the current best practices.}
      \resumeItemListEnd

    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Research and Teaching Assistant}{Jan 2012 -- Dec 2013}
      \resumeItemListStart
        \resumeItem{Research Assistant -- Machine Learning}
          {Research on machine learning for portfolio hedging and replication algorithms. Modeling low-risk \& continuous-return strategies. Developed the Python library QSTK.}
        \resumeItem{Teaching Assistant -- Computational Investing}
          {The online course on Coursera, had more than 100,000 students enrolled. It was featured on the 11 Alive News and the Atlanta Journal Constitution. Involved in creating assignment, exams and conducting recitation sessions. Also taught the on-campus version of the course.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{QuantSoftware Toolkit}
      {Open source Python library for financial data analysis and machine learning for finance.}
    \resumeSubItem{GitHub Visualization}
      {Data visualization of Git log data using D3 to analyze project trends over time.}
    \resumeSubItem{Recommendation System}
      {Music and movie recommender systems using collaborative filtering on public datasets.}
    \resumeSubItem{Mac Setup}
      {Book that gives step-by-step instructions on setting up developer environment on macOS.}
  \resumeSubHeadingListEnd

%
%--------SKILLS------------
%\section{Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, JavaScript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
